Automating Verification of MPC Security

### 2023-06-20 popl24/hyperprop.tex
typos hyperprop.tex

In this section we formulate a new hyperproperty that we show is sound
for passive security in the real/ideal model, called
\emph{noninterference modulo output ($\NIMO$)}. We do not claim
completeness with respect to passive security, but soundness
guarantees that enforcement of $\NIMO$ in our analyses implies passive
security. In Section \ref{section-bruteforce} we show how $\NIMO$ can
be automatically enforced in a brute-force manner, and in Section
\ref{section-composition} we show how $\NIMO$ can be refined to obtain
compositional properties supporting efficient, scalable enforcement of
complex protocols that incorporate modular subprotocols, with a
specific use-case of Yao's Garbled Circuits (YGC) as an example where
garbled gates are the compositional units.  The latter methodology
demonstrates a particular advantage of our hyperproperty formulation.

\subsection{Passive Security and the Real/Ideal Model} \dnote{would shortening the background info on how simulator model works be a bad idea?} Here we
briefly summarize the formal definition of MPC security. For a
more detailed discussion the reader is referred to \cite{XXX}.
In this paper we will consider the \emph{passive} aka
semi-honest aka honest-but-curious variant. In this threat
model, protocol participants can be corrupted, but all clients
follow the rules of the protocol- as opposed to the
\emph{active} aka malicious variant where participants
are allowed to break these rules. In the passive model, the
vulnerability is through information leaked to the adversary
through the views of corrupted participants. While the passive
model also assumes that any clients can potentially be
corrupted, it assumes that no more than half will be-
i.e., it assumes an \emph{honest majority}.

@@

From an information flow perspective, we can say that a $\NIMO$
protocol does not release information beyond what is declassified
via the public output. From a real/ideal perspective, we can
observe that $\NIMO$ implies that the simulator can use
the protocol itself to reconstruct the distribution of adversarial
views. That is, given the output of the ideal functionality
$\idealf(\store_S)$, the simulator can randomly choose any
$\store'$ such that $\store' =_C \store$ and $\idealf(\store'_S) =
\idealf(\store_S)$ and run the protocol with initial memory $\store'$-
$\NIMO$ guarantees ideal reconstruction of the real-world corrupt views. 
 However, there is a subtlety here in that the adversary
must be able to tractably reconstruct this knowledge. This is not
generally true, in particular if $\idealf$ is a 1-way
function. Define:
\begin{definition}[Ideal Knowledge]
  Given a functionality $\idealf$ and output value $v$, the associated
  \emph{ideal knowledge}, denoted $\ik(\idealf,v)$ is:
  $$
  \{ \store\ |\ \idealf(\store) = v \}
  $$
  We say that $\idealf$ is \emph{invertible} iff $\ik(\idealf, v)$ for all
  $v$ can be computed tractably.
\end{definition}
Now we can show our main result, that noninterference modulo output,
together with the assumption that $\idealf$ is invertible, implies
passive security of a protocol.
\begin{theorem}
  \label{theorem-nimo}
  Assume given invertible $\idealf$ and a protocol $\prog$ that
  correctly implements $\idealf$.  If $\NIMO(\prog)$
  then $\prog$ is passive secure.
\end{theorem}

\begin{proof}
  Let $H$ and $C$ be an arbitrary partition of the federation and
  suppose $\prog$ satifies noninterference modulo output. Let
  $\iov(\prog) = (V,S)$ and $\flips(\prog) = F$ with output view $x
  \in V$ and let $\store$ be an arbitrary member of $\mems(S \cup
  F)$. Then the distribution of adversarial views in the real world
  is, by definition:
  $$\margd{(\condd{\progd(\prog)}{\store_S})}{V_C}$$

>>>>

In this section, we formulate a new hyperproperty that we show is sound
for passive security in the real/ideal model, called
\emph{noninterference modulo output ($\NIMO$)}. We do not claim
completeness with respect to passive security, but soundness
guarantees that enforcement of $\NIMO$ in our analyses implies passive
security. In Section \ref{section-bruteforce} we show how $\NIMO$ can
be automatically enforced in a brute-force manner, and in Section
\ref{section-composition} we show how $\NIMO$ can be refined to obtain
compositional properties supporting efficient, scalable enforcement of
complex protocols that incorporate modular subprotocols, with a
specific use-case of Yao's Garbled Circuits (YGC) as an example where
garbled gates are the compositional units.  The latter methodology
demonstrates a particular advantage of our hyperproperty formulation.

\subsection{Passive Security and the Real/Ideal Model} \dnote{would shortening the background info on how simulator model works be a bad idea?} Here we
briefly summarize the formal definition of MPC security. For a
more detailed discussion the reader is referred to \cite{XXX}.
In this paper, we will consider the \emph{passive} aka
semi-honest aka honest-but-curious variant. In this threat
model, protocol participants can be corrupted, but all clients
follow the rules of the protocol- as opposed to the
\emph{active} aka malicious variant where participants
are allowed to break these rules. In the passive model, the
vulnerability is through information leaked to the adversary
through the views of corrupted participants. While the passive
model also assumes that any clients can potentially be
corrupted, it assumes that no more than half will be-
i.e., it assumes an \emph{honest majority}.

@@

From an information flow perspective, we can say that a $\NIMO$
protocol does not release information beyond what is declassified
via the public output. From a real/ideal perspective, we can
observe that $\NIMO$ implies that the simulator can use
the protocol itself to reconstruct the distribution of adversarial
views. That is, given the output of the ideal functionality
$\idealf(\store_S)$, the simulator can randomly choose any
$\store'$ such that $\store' =_C \store$ and $\idealf(\store'_S) =
\idealf(\store_S)$ and run the protocol with initial memory $\store'$-
$\NIMO$ guarantees ideal reconstruction of the real-world corrupt views. 
 However, there is a subtlety here in that the adversary
must be able to tractably reconstruct this knowledge. This is not
generally true, in particular, if $\idealf$ is a 1-way
function. Define:
\begin{definition}[Ideal Knowledge]
  Given a functionality $\idealf$ and output value $v$, the associated
  \emph{ideal knowledge}, denoted $\ik(\idealf,v)$ is:
  $$
  \{ \store\ |\ \idealf(\store) = v \}
  $$
  We say that $\idealf$ is \emph{invertible} iff $\ik(\idealf, v)$ for all
  $v$ can be computed tractably.
\end{definition}
Now we can show our main result, that noninterference modulo output,
together with the assumption that $\idealf$ is invertible, implies
passive security of a protocol.
\begin{theorem}
  \label{theorem-nimo}
  Assume given invertible $\idealf$ and a protocol $\prog$ that
  correctly implements $\idealf$.  If $\NIMO(\prog)$
  then $\prog$ is passive secure.
\end{theorem}

\begin{proof}
  Let $H$ and $C$ be an arbitrary partition of the federation and
  suppose $\prog$ satisfies noninterference modulo output. Let
  $\iov(\prog) = (V,S)$ and $\flips(\prog) = F$ with output view $x
  \in V$ and let $\store$ be an arbitrary member of $\mems(S \cup
  F)$. Then the distribution of adversarial views in the real world
  is, by definition:
  $$\margd{(\condd{\progd(\prog)}{\store_S})}{V_C}$$
